Blocks of extended ancestry around selected loci in hybrid zones

### 2016-02-27 drafts/hybrid_zone.tex
various
added supp fig on comparison of clines t

The simulations are executed in R, with scripts available on
\url{https://github.com/asedghifar/hybridzones}.

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim}
\caption{
Frequency of ancestry B,
across geography and at several physical positions on the genome,
at $T=100$ generations after secondary contact. 
\plr{what is $s$?}
Each line represents a locus some distance $r$ away from the true target of selection, and $r=0$ represents the locus that is under selection. Grey lines represent the same positions from a simulation with
identical parameters except $s=0$.
    \plr{Add same figure for some different time points and maybe values of $s$ to the supplement.} 
}\label{alleleFreq_tau100}
\end{figure}

>>>>

The simulations are executed in R, with scripts available on
\url{https://github.com/asedghifar/hybridzones}.
\plr{if I'm to be the corresp author, put this to \url{https://github.com/petrelharp/clinal-lineages}?}

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim}
\caption{
    Frequency of ancestry B,
    across geography and at several physical positions on the genome,
    at $T=100$ generations after secondary contact,
    and with $s=0.1$.
    Each line represents a locus some distance $r$ away from the true target of selection, 
    and $r=0$ represents the locus that is under selection. Grey lines represent the same positions from a simulation with
    identical parameters except $s=0$.
    Corresponding theoretical quantities are shown juxtaposed in Figure \ref{sfig:alleleFreq_tau100_comparison}.
    \plr{Add same figure for some different time points and maybe values of $s$ to the supplement.} 
}\label{alleleFreq_tau100}
\end{figure}

### 2016-02-27 drafts/supplement.tex
added supp fig on comparison of clines t

>>>>

\begin{figure}
    \includegraphics{figs/alleleFrequencies_sim_comparison}
    \caption{
        \textbf{Comparison of simulated to theoretical clines:}
        As in Figure \ref{alleleFreq_tau100},
        frequency of ancestry B,
        across geography and at several physical positions on the genome,
        at $T=100$ generations after secondary contact,
        and at $s=0.1$.
        Dotted lines are expected frequencies of $B$ ancestry $1-q(x,t,r)$
        (unconditional on the ancestry of the linked allele), computed numerically.
        Each line represents a locus some distance $r$ away from the true target of selection, 
        and $r=0$ represents the locus that is under selection. Grey lines represent the same positions from a simulation with
        identical parameters except $s=0$.
    }\label{sfig:alleleFreq_tau100_comparison}
\end{figure}
